Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-18 doc/report/intro.tex
update intro

However, we argue that traditional graphical user interface (GUI) on mobile platforms still imposes difficulty in interacting with physical objects. Imagine when we have all the control panel integrated into iPhone, users then need to browse a list of possible icons and select the right one. Even if you can create widget to simplify the browsing overhead, such as on Android platform, the problem still holds since squeezing physically distributed objects onto a-few-inch screen is not the right approach. In an ideal system, the user should be able to express their interest of interaction in a more direct way. On the other hand, taking out the phones (or even simply locating them when at home) is relatively time-consuming. According to a study in \cite{Ashbrook:2008:QIM:1357054.1357092}, 4 seconds are required on average just to get a phone out of the pocket or hip holster, not to mention the time to choose the target and initiate interaction. This project is trying to propose a new way of interacting with physical objects without losing attention, essentially solving the ``addressing'' problem in interacting with physical devices around.

@@

Some direct gesture include looking, pointing and reaching, and there is one interesting paper \cite{Merrill:2007:ALP:1758156.1758158} which put sensors to users' ears and fingers to detect their intention. And this information is fed back to the system to assist user in browsing physical objects. Our approach borrows idea from this by putting sensors on users' body, however, we enable the direct interaction rather than just passive sensing. The other major difference is that we choose to use glass form factor for such attention expression. Firstly, line of sight is easier to detect on glasses, rather than earpiece. And this is also more intuitive to users that when they are looking at something, they might be interested in that, and this information is captured by a on-glass sensor. Second, with the release of Google Glass, we believe that it could serve as the enabling hardware platform. Though in this paper, we will still present some of our thoughts on ``what if we have an advanced glass and various sensors'', we focus most of the discussion on our prototype which uses IR to express users' interst, XBee radio for device communication, and a slider for users' gesture. We admit that improvements are huge to make the device more compact and compelling, the system more robust, and the size smaller and more convenient. But for this semester project, our goal (for us) is to explore the possibility of enabling direct interaction with physical objects, learn how to prototype novel interaction device on our own, and apply what we have learned and discussed in class about human computer interaction into a real project.

>>>>

However, we argue that traditional graphical user interface (GUI) on mobile platforms still imposes difficulty in interacting with real-world objects. Imagine when we have all the control panel integrated into iPhone, users then need to browse a list of possible icons and select the right one. Even if you can create widget to simplify the browsing overhead, such as on Android platform, the problem still holds since squeezing physically distributed objects onto a few-inch screen is not an intuitive mapping. In an ideal system, the user should be able to express their interest of interaction in a more direct way. In addition, taking out the phones (including locating them, turn on the screen, perhaps entering the passcode, and open the application) is relatively time-consuming. According to a study in \cite{Ashbrook:2008:QIM:1357054.1357092}, 4 seconds are required on average just to get a phone out of the pocket or hip holster, not to mention the time to choose the target and initiate interaction. This project is trying to propose a new way of interacting with physical objects without losing attention, essentially solving the ``addressing'' problem in interacting with physical devices around.

@@

Some direct gesture include looking, pointing and reaching, and there is one interesting paper \cite{Merrill:2007:ALP:1758156.1758158} which put sensors to users' ears and fingers to detect their intention. And this information is fed back to the system to assist user in browsing physical objects. Our approach was inspired by this paper. We utilize sensors on users' body, however, we enable the direct interaction rather than just passive sensing. The other major difference is that we choose to use glass form factor for such attention expression. Firstly, line of sight is easier to detect on glasses, rather than earpiece. And this is also more intuitive to users that when they are looking at something, they might be interested in that, and this information is captured by a on-glass sensor. Second, with the release of Google Glass, we believe that it could serve as the enabling hardware platform. Though in this paper, we will still present some of our thoughts on ``what if we have an advanced glass and various sensors'', we focus most of the discussion on our prototype which uses IR to express users' interst, XBee radio for device communication, and a slider for users' gesture. We recognize that there is a great room of improvement for making the system more robust and the device more compact. But for this semester project, our goal (for us) is to explore the possibility of enabling direct interaction with physical objects, learn how to prototype novel interaction device on our own, and apply what we have learned and discussed in class about human computer interaction into a real project.
